Evaluating an epidemiologically motivated surrogate model of a multi-model ensemble

### 2022-10-12 paper/paper.Rmd
correct paper numbering

```{r observations}
observations <- data.table(
  No. = 1:5,
  Observation = c(
    "Robust to daily reporting artefacts",
    "Some ability to forecast future trend changes",
    "Less reactive to apparent observed changes in trend",
    "Sharper forecasts",
    "A tendency towards underprediction",
    "Modelling the reporting process appears to have little impact"
  )
)

>>>>

```{r observations}
observations <- data.table(
  No. = 1:6,
  Observation = c(
    "Robust to daily reporting artefacts",
    "Some ability to forecast future trend changes",
    "Less reactive to apparent observed changes in trend",
    "Sharper forecasts",
    "A tendency towards underprediction",
    "Modelling the reporting process appears to have little impact"
  )
)
